Quantifying the manageability of pollination networks in an invasion context

### 2017-02-28 paper/draft_2.Rmd
New title and metadata

---
title: "The manageability of pollination networks in an invasion context"
classoption: a4paper
csl: ecology-letters.csl
output:
  pdf_document:
    fig_crop: no
  html_document: default
  word_document: default
header-includes:
- \usepackage{setspace}
- \usepackage{float}
- \usepackage{booktabs}
- \usepackage{caption} 
- \usepackage{lineno}
documentclass: artikel1
bibliography: references.bib
---

@@

* **Authorship:** DBS conceived the idea; EFC, DBS and KLW contributed to the development of the theoretical framework. EFC performed all analysis. EFC and DBS wrote the manuscript.

>>>>

---
title: "Quantifying the manageability of pollination networks in an invasion context"
classoption: a4paper
csl: ecology-letters.csl
output:
  pdf_document:
    fig_crop: no
  html_document: default
  word_document: default
header-includes:
- \usepackage{setspace}
- \usepackage{float}
- \usepackage{booktabs}
- \usepackage{caption} 
- \usepackage{lineno}
documentclass: artikel1
bibliography: references.bib
---

@@

* **Authorship:** DBS conceived the idea; all authors contributed to the development of the theoretical framework. EFC performed all analysis. EFC and DBS wrote the manuscript.
